Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-08 WSSSPE4_report/survey_details.tex
small caption changes
fixed formatting for combined figure & table

\begin{figure}[h!]
    \CenterFloatBoxes
    \begin{floatrow}
    \ffigbox[\FBwidth]{%
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig4rev}%
    }{%
        \captionsetup{width=\linewidth}
        \caption{What part of the meeting was the most valuable?
        \label{fig:SFig4}}%
    }
    \hfill
    \killfloatstyle\capbtabbox[\linewidth]{%
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}ll@{}}
    \toprule
    Answer & Count \\
    \midrule
    Plenary & 19 \\
    Panel & 14 \\
    Working Groups & 36 \\
    Other & 5 \\
    Total & 74 \\
    \bottomrule
    \end{tabular}
    }{%
        \caption{Value of meeting parts}%
    }
    \end{floatrow}
\end{figure}

@@

\begin{figure}[h!]
    \CenterFloatBoxes
    \centering
    \begin{floatrow}
    \ffigbox[\FBwidth]{%
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig5rev}%
    }{%
        \captionsetup{width=\linewidth}
        \caption{Would you be interested in joining a professional society
        focused around the topics of WSSSPE?
        \label{fig:SFig5}}%
    }
    %\hfill
    ~
    \killfloatstyle\capbtabbox[\linewidth]{%
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}ll@{}}
    \toprule
    Answer & Count \\
    \midrule
    Yes & 24 \\
    No & 3 \\
    Maybe & 18 \\
    Total & 45 \\
    \bottomrule
    \end{tabular}
    }{%
        \caption{A WSSSPE society?}%
        \label{tab:survey_society}
    }
    \end{floatrow}
\end{figure}

@@

\begin{figure}[h!]
    \CenterFloatBoxes
    \centering
    \begin{floatrow}
    \ffigbox[\FBwidth]{%
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig6rev}%
    }{%
        \captionsetup{width=\linewidth}
        \caption{Will you be part of a working group  with colleagues going
        forward  on a topic addressed at WSSSPE?
        \label{fig:SFig6}}%
    }
    ~
    \killfloatstyle\capbtabbox[\linewidth]{%
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}ll@{}}
    \toprule
    Answer & Count \\
    \midrule
    Yes & 32 \\
    No & 4 \\
    Maybe & 9 \\
    Total & 45 \\
    \bottomrule
    \end{tabular}
    }{%
        \caption{Continuing working groups?}%
        \label{tab:survey_continuing_wgs}
    }
    \end{floatrow}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig4rev}%
    \end{tabular}
    \qquad
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}lc@{}}
    \toprule
    Answer & Count \\
    \midrule
    Plenary & 19 \\
    Panel & 14 \\
    Working Groups & 36 \\
    Other & 5 \\
    Total & 74 \\
    \bottomrule
    \end{tabular}
    \caption{Responses to ``What part of the meeting was the most valuable?''}
    \label{fig:SFig4}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig5rev}%
    \end{tabular}
    \qquad
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}lc@{}}
    \toprule
    Answer & Count \\
    \midrule
    Yes & 24 \\
    No & 3 \\
    Maybe & 18 \\
    Total & 45 \\
    \bottomrule
    \end{tabular}
    \caption{Responses to ``Would you be interested in joining a professional
    society focused around the topics of WSSSPE?''}
    \label{fig:SFig5}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig6rev}%
    \end{tabular}
    \qquad
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}lc@{}}
    \toprule
    Answer & Count \\
    \midrule
    Yes & 32 \\
    No & 4 \\
    Maybe & 9 \\
    Total & 45 \\
    \bottomrule
    \end{tabular}
    \caption{Responses to ``Will you be part of a working group  with colleagues
    going forward  on a topic addressed at WSSSPE?''}
    \label{fig:SFig6}
\end{figure}
